Paper Title*\\

### 2019-05-07 latex-template/paper.tex
testing, handle error in npm/cli file
Updated abstract

\begin{abstract}
JavaScript is the most dominant language used to develop front-ends and back-end in multiple web applications. This is because of multiple features it brings with it along the lines of event-driven and asynchronous programming; which are one of the most crucial aspects when developing a smooth and fast web interface. One of the features that helps maintain flow of instructions in asynchronous language is callbacks or higher order functions. However, a poor understanding of callbacks can result in many complexities such as nested callbacks (also referred to as callback hell). Another problem that nested callbacks can cause is lose of benefit of asynchrony since execution of program becomes linear when independent functions are nested into callbacks of other function calls. We present a tool developed in JavaScript that checks for independent instructions inside callbacks and refactors them outside of callbacks.
\end{abstract}

@@

Rest of the articles is divided into following order:
\begin{itemize}
	\item Methodology
	\item Implementation
	\item Limitations and Challenges
	\item Related Work
	\item Conclusion

>>>>

\begin{abstract}
JavaScript is the most dominant language used to develop front-ends and back-end in multiple web applications. This is because of multiple features it brings with it along the lines of event-driven and asynchronous programming; which are one of the most crucial aspects when developing a smooth and fast web interface. One of the features that helps maintain flow of instructions in asynchronous language is callbacks or higher order functions. However, a poor understanding of callbacks can result in many complexities such as nested callbacks (also referred to as callback hell). Another problem that nested callbacks can cause is loss of the benefit of asynchrony since execution of program becomes linear when independent functions are nested into callbacks of other function calls. One major factor which causes the loss of asynchrony, are instructions that are being used within a callback but can be executed before the callback is actually called. We present a technique that analyzes code and is able to suggest refactorable instructions within callbacks based upon where these instructions are declared and used. We tested our tool on multiple JavaScript files.
\end{abstract}

@@

Rest of the articles is divided into following order:
\begin{itemize}
	\item Methodology
	\item Implementation
	\item Testing
	\item Limitations and Challenges
	\item Related Work
	\item Conclusion
